---
title: "XML Analysis Template"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document: default
  html_document:
    css: css/custom.css
---

```{r cache=FALSE, echo=FALSE}
# Parameters
# Use this chunk to set the parameters for a test run.
use.case.titles <- c("__Digital Forensics XML (DFXML)__",
                     "__Packet Details Markup Language (PDML)__",
                     "__OpenStreetMap__")
use.case <- "pdml"
use.case.title <- use.case.titles[2]
export.images <- FALSE
image.folder <- file.path("..","reports","plots")

library(knitr)
library(ggplot2)
library(reshape2)
library(scales)
library(plyr)
library(grid)

input.file <- file.path("..", "..", "data", paste0(use.case, "_results.csv"))
source("../utilities/util.R")

opts_chunk$set(fig.width=8, fig.height=4) # Quick adjustment for landscape figures - only affects knitr output
options(warn = -1) # Prevent ggplot2 from dumping warnings to knitr output

df <- read.csv(input.file)

counter <- 1 # controls what letter is assigned to a focus question, as well as the letter appended to plot export filenames
```

# Results for `r use.case.title`  Use Case

```{r echo=FALSE}
# Extra code for faceting across use-cases.

# df1 <- read.csv(file.path("..", "..", "data", "owm_results.csv"))
# dfc1 <- dcast(df1, file ~ variable)
# uc <- character(length(dfc1[,1]))
# uc[1:length(uc)] <- "OWM"
# dfc1$use.case <- uc
# 
# df2 <- read.csv(file.path("..", "..", "data", "gpx_results.csv"))
# dfc2 <- dcast(df2, file ~ variable)
# uc <- character(length(dfc2[,1]))
# uc[1:length(uc)] <- "GPX"
# dfc2$use.case <- uc
# 
# dfc <- rbind(dfc1, dfc2)
# 
# s <- c("xml.bitpacked_exi",
#        "xml.schema_compress_exi")
# 
# df.temp <- melt(dfc, id=c("file", "use.case"))
# 
# p <- faceted.filesize.vs.compaction(df=df.temp,
#                                baseline="xml",
#                                series=s,
#                                facet="use.case",
#                                x.range="auto")
# p <- prettify.plot(p, legend.placement="top.right")
# print(p)
```

### EXI Exploratory

`r LETTERS[counter]`. How do the primary EXI modes compare for schemaless encodings?

```{r, echo=FALSE}
s <- c("xml.bitpacked_exi",
       "xml.precompress_exi",
       "xml.compress_exi")
p <- filesize.vs.compaction(df=df, baseline="xml", series=s, x.range="log")
p <- prettify.plot(p, legend.placement="bottom.left")
print(p)

if(export.images){ save.for.print(image.folder, use.case, paste0("plot-",letters[counter])) }
counter <- counter + 1
```

$\pagebreak$

`r LETTERS[counter]`. How do the primary EXI ‘modes’ compare for schema-informed encodings?

```{r, echo=FALSE}
s <- c("xml.schema_bitpacked_exi",
       "xml.schema_precompress_exi",
       "xml.schema_compress_exi")
p <- filesize.vs.compaction(df=df, baseline="xml", series=s, x.range="log")
p <- prettify.plot(p, legend.placement="bottom.left")
print(p)

if(export.images){ save.for.print(image.folder, use.case, paste0("plot-",letters[counter])) }
counter <- counter + 1
```

$\pagebreak$

`r LETTERS[counter]`. Does the ‘strict’ option significantly improve compaction for schema-informed encodings?

```{r, echo=FALSE}
s <- c("xml.schema_bitpacked_exi",
       "xml.strict_bitpacked_exi",
       "xml.schema_compress_exi",
       "xml.strict_compress_exi")
p <- filesize.vs.compaction(df=df, baseline="xml", series=s, x.range="log")
p <- prettify.plot(p, legend.placement="bottom.left")
print(p)

if(export.images){ save.for.print(image.folder, use.case, paste0("plot-",letters[counter])) }
counter <- counter + 1
```

$\pagebreak$

`r LETTERS[counter]`. Do any of the tested compression algorithms perform better on a schemaless, precompress EXI document than the standard DEFLATE?

```{r, echo=FALSE}
s <- c("xml.precompress_exi.zip",
       "xml.precompress_exi.gz",
       "xml.precompress_exi.bz2")
p <- filesize.vs.compaction(df=df, baseline="xml.compress_exi", series=s, x.range="log")
p <- prettify.plot(p, legend.placement="bottom.left")
print(p)

if(export.images){ save.for.print(image.folder, use.case, paste0("plot-",letters[counter])) }
counter <- counter + 1
```

$\pagebreak$

`r LETTERS[counter]`. Do any of the tested compression algorithms perform better on a schema-informed, precompress EXI document than the standard DEFLATE?

```{r, echo=FALSE}
s <- c("xml.schema_precompress_exi.zip",
       "xml.schema_precompress_exi.gz",
       "xml.schema_precompress_exi.bz2")
p <- filesize.vs.compaction(df=df, baseline="xml.schema_compress_exi", series=s, x.range="log")
p <- prettify.plot(p, legend.placement="bottom.left")
print(p)

if(export.images){ save.for.print(image.folder, use.case, paste0("plot-",letters[counter])) }
counter <- counter + 1
```

$\pagebreak$

## Binary-comparisons

`r LETTERS[counter]`. Which EXI encoding is the most compact?

```{r, echo=FALSE}
s <- c("xml.strict_compress_exi",
            "xml.strict_bitpacked_exi",
            "xml.compress_exi")
p <- filesize.vs.compaction(df=df, baseline="xml", series=s, x.range="log")
p <- prettify.plot(p, legend.placement="bottom.left")
print(p)

if(export.images){ save.for.print(image.folder, use.case, paste0("plot-",letters[counter])) }
counter <- counter + 1
```

$\pagebreak$

`r LETTERS[counter]`. For a network already using gzip, do any of the EXI encodings offer improvements?

```{r, echo=FALSE}
s <- c("xml.strict_compress_exi",
            "xml.strict_bitpacked_exi",
            "xml.compress_exi")
p <- filesize.vs.compaction(df=df, baseline="xml.gz", series=s, x.range="log")
p <- prettify.plot(p, legend.placement="top.left")
print(p)

if(export.images){ save.for.print(image.folder, use.case, paste0("plot-",letters[counter])) }
counter <- counter + 1
```
