---
title: "XML Analysis Template"
output: 
  html_document:
    css: css/custom.css
---

__Parameters__

Use this chunk to set the parameters for a test run. `input.file` is the path to an input file in the above CSV format (using the OS-independent `file.path()` function.


```{r}
input.file <- file.path("..", "..", "data", "dfxml_results.csv")
```


```{r cache=FALSE, include=FALSE}
library(knitr)
library(ggplot2)
library(reshape2)
library(scales)
library(plyr)
library(grid)

source("../utilities/util.R")

opts_chunk$set(fig.width=8, fig.height=4) # Quick adjustment for landscape figures - only affects knitr output
options(warn = -1) # Prevent ggplot2 from dumping warnings to knitr output

df <- read.csv(input.file)

```

# Focus questions
****

### EXI Exploratory

How do the primary EXI ‘modes’ compare for schemaless encodings?

```{r, echo=FALSE}
s <- c("xml.bitpacked_exi",
       "xml.precompress_exi",
       "xml.compress_exi")
p <- filesize.vs.compaction(df=df, baseline="xml", series=s, x.range="log")
p <- prettify.plot(p, legend.placement="top.right")
print(p)
```

How do the primary EXI ‘modes’ compare for schema-informed encodings?

```{r, echo=FALSE}
s <- c("xml.schema_bitpacked_exi",
       "xml.schema_precompress_exi",
       "xml.schema_compress_exi")
p <- filesize.vs.compaction(df=df, baseline="xml", series=s, x.range="log")
p <- prettify.plot(p, legend.placement="bottom.left")
print(p)
```

Does the ‘strict’ option significantly improve compaction for schema-informed encodings?

```{r, echo=FALSE}
# s <- c("xml.schema_bitpacked_exi",
#        "xml.strict_bitpacked_exi",
#        "xml.schema_compress_exi",
#        "xml.strict_compress_exi")
# p <- filesize.vs.compaction(df=df, baseline="xml", series=s)
# print(p)
```

Do any of the tested compression algorithms perform better on a schemaless, precompress EXI document than the standard DEFLATE?

```{r, echo=FALSE}
s <- c("xml.precompress_exi.zip",
       "xml.precompress_exi.gz",
       "xml.precompress_exi.bz2")
p <- filesize.vs.compaction(df=df, baseline="xml.compress_exi", series=s, x.range="log")
p <- prettify.plot(p, legend.placement="bottom.right")
print(p)
```

Do any of the tested compression algorithms perform better on a schema-informed, precompress EXI document than the standard DEFLATE?

```{r, echo=FALSE}
s <- c("xml.schema_precompress_exi.zip",
       "xml.schema_precompress_exi.gz",
       "xml.schema_precompress_exi.bz2")
p <- filesize.vs.compaction(df=df, baseline="xml.schema_compress_exi", series=s, x.range="log")
p <- prettify.plot(p, legend.placement="bottom.right")
print(p)
```

## Binary-comparisons

Which binary format is the most compact?

```{r, echo=FALSE}
# s <- c("xml.strict_compress_exi",
#             "xml.strict_bitpacked_exi",
#             "xml.compress_exi")
# p <- filesize.vs.compaction(df=df, baseline="xml", series=s, x.range="auto")
# print(p)
```

For a network already using gzip, do any of the binary formats offer improvements?

```{r, echo=FALSE}
# s <- c("xml.strict_compress_exi",
#             "xml.strict_bitpacked_exi",
#             "xml.compress_exi")
# p <- filesize.vs.compaction(df=df, baseline="xml.gz", series=s, x.range="auto")
# print(p)
```