---
title: "Office Open XML Analysis Template"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document: default
  html_document:
    css: css/custom.css
---

```{r cache=FALSE, echo=FALSE}
# Parameters
# Use this chunk to set the parameters for a test run.
selection <- 3
export.images <- TRUE
image.folder <- file.path("..","reports","plots","ooxml")

use.cases <- c("docx", "xlsx", "pptx")
use.case.titles <- c("__Office Open XML Document__",
                     "__Office Open XML Spreadsheet__",
                     "__Office Open XML Presentation__")
use.case <- use.cases[selection]
use.case.title <- use.case.titles[selection]

library(knitr)
library(ggplot2)
library(reshape2)
library(scales)
library(plyr)
library(grid)

input.file <- file.path("..", "..", "data", paste0(use.case, "_results.csv"))
source("../utilities/util.R")

opts_chunk$set(fig.width=8, fig.height=4) # Quick adjustment for landscape figures - only affects knitr output
options(warn = -1) # Prevent ggplot2 from dumping warnings to knitr output

df <- read.csv(input.file)

counter <- 1 # controls what letter is assigned to a focus question, as well as the letter appended to plot export filenames
```

# Results for `r use.case.title`  Use Case

`r LETTERS[counter]`. Does EXI improve compaction for Microsoft Office documents saved in the Strict Open XML format?

```{r, echo=FALSE}
if (selection == 1) {
  s <- c("docx.zip",
         "doce")
  p <- filesize.vs.compaction(df=df, baseline="docx", series=s, x.range="log")
} else if (selection == 2) {
  s <- c("xlsx.zip",
         "xlse")
  p <- filesize.vs.compaction(df=df, baseline="xlsx", series=s, x.range="log")  
} else if (selection == 3) {
  s <- c("pptx.zip",
         "ppte")
  p <- filesize.vs.compaction(df=df, baseline="pptx", series=s, x.range="log")  
}


p <- prettify.plot(p, legend.placement="bottom.right")
print(p)

if(export.images){ save.for.print(image.folder, use.case, paste0("plot-",letters[counter])) }
counter <- counter + 1
```

```{r}

df1 <- read.csv(file.path("..", "..", "data", "docx_results.csv"))
dfc1 <- dcast(df1, file ~ variable)
dfc1 <- rename(dfc1, c("docx"="office", "doce"="exi", "docx.zip"="office.zip"))
facet.var <- character(length(dfc1[,1]))
facet.var[1:length(facet.var)] <- "Word"
dfc1$facet <- facet.var

df2 <- read.csv(file.path("..", "..", "data", "xlsx_results.csv"))
dfc2 <- dcast(df2, file ~ variable)
dfc2 <- rename(dfc2, c("xlsx"="office", "xlse"="exi", "xlsx.zip"="office.zip"))
facet.var <- character(length(dfc2[,1]))
facet.var[1:length(facet.var)] <- "Excel"
dfc2$facet <- facet.var

df3 <- read.csv(file.path("..", "..", "data", "pptx_results.csv"))
dfc3 <- dcast(df3, file ~ variable)
dfc3 <- rename(dfc3, c("pptx"="office", "ppte"="exi", "pptx.zip"="office.zip"))
facet.var <- character(length(dfc3[,1]))
facet.var[1:length(facet.var)] <- "PowerPoint"
dfc3$facet <- facet.var

dfc <- rbind(dfc1, dfc2, dfc3)

s <- c("exi")

df.temp <- melt(dfc, id=c("file", "facet"))

p <- faceted.filesize.vs.compaction(df=df.temp,
                               baseline="office",
                               series=s,
                               facet="facet",
                               x.range="log")
p <- prettify.plot(p, legend.placement="bottom.right")
print(p)

if(export.images){ save.for.print(image.folder, use.case, paste0("plot-",letters[counter])) }
counter <- counter + 1
counter <- counter + 1